\documentclass[a4paper]{article}
\usepackage{appendix}
\usepackage{cleveref}
\begin{document}

\title{The Constitution of the UWA Programming Competition Society}
\date{}

\maketitle


\section{Name}
\begin{enumerate}
	\item The name of the Society shall be: \textbf{The UWA Programming Competition Society}.
    \item The Society will also go by the abbreviations \textbf{PCS} and \textbf{UWA PCS}.
\end{enumerate}


\section{Definitions}
\begin{enumerate}
    \item Guild --- the Guild of Undergraduates of the University of Western Australia.
    \item University --- the University of Western Australia.
    \item the Society --- the UWA Programming Competition Society.
    \item Regulation --- a rule, passed by Committee, with ongoing consequences to the Society.
    \item Fresher --- a first time member of the club.
\end{enumerate}


\section{Objectives} \label{sec:objectives}
\begin{enumerate}
    \item To encourage and facilitate competitive programming at the University and within the wider community.
    \item To become and remain affiliated with the Societies Council of the Guild.
    \item To encourage and facilitate computer science and mathematics education at the University and within the wider community.
    \item To encourage and facilitate the holding of events and functions beneficial to Objectives of the Society.
    \item To encourage and promote cooperation between the Society and other societies and community-based organizations representative of the Society's interests.
    \item To ensure that the Society shall not by way of gift transmit any monies, grants or property to any person except in the direct cause of these Objectives and as detailed in \cref{sec:dissolution}.
\end{enumerate}


\section{Membership of the Society}
\begin{enumerate}
    \item Society membership is targeted at, but not restricted to:
    \begin{enumerate}
        \item Students of the University
        \item Members of the Guild
        \item Past members of the Society
    \end{enumerate}
    \item Membership shall not be made available to persons who have been expelled (see \cref{sec:expulsion}).
    \item Honorary life membership may be conferred by a two-thirds majority of a General Meeting upon any member who has performed outstanding service to the Society.
    \item The annual subscription for members shall be set by the Committee of the Society, subject to any restrictions set by the Guild.
    \item A financial member is a member who has paid their annual subscription for this year.
    \item Financial memberships expire 1 day prior to the holding of the Annual General Meeting in the subsequent year from its payment (see \cref{sec:AGMs}).
\end{enumerate}


\section{The Committee} \label{sec:committee}
\begin{enumerate}
	\item The Committee of the Society shall consist of:
    \begin{enumerate}
    	\item The executive office bearers:
        \begin{itemize}
          \item President
          \item Vice-President
          \item Treasurer
          \item Secretary 
        \end{itemize}
        \item The non-executive Committee members:
        \begin{itemize}
            \item Fresher Representative
        	\item Three Ordinary Committee Members
        \end{itemize}
    \end{enumerate}
    \item After the Committee has been elected it shall proceed to appoint from amongst its members a delegate to any subsidiary council to which the Society is affiliated, such as the Societies Council of the Guild.
    \item The Committee members shall remain in office until the next Annual General Meeting or until they lose the confidence of a General Meeting, at which their position is declared vacant (see \cref{sec:committee}, \cref{sub:removing_committee}).
    \item \label{sub:removing_committee} By two-thirds majority vote the General Meeting may remove any member of the Committee from office. They must then elect a member to that role, following the rules laid out in \cref{sec:AGMs}.
    \item If a Committee member ceases to meet the eligibility requirements for their position, as detailed in \cref{sec:AGMs}, then they shall cease to hold office and the position shall be declared vacant.
    \item \label{sub:committee_resign} If a Committee member resigns or ceases to hold office for any reason, then the vacancy shall either:
    \begin{enumerate}
        \item Be filled through appointment by Committee from the financial membership of the club, subject to review at the next General Meeting.
        \begin{enumerate}
            \item When reviewing, a simple majority vote of the General Meeting will confirm the appointment. If such a vote fails then the position must be immediately filled by election (as per \cref{sec:AGMs}).
        \end{enumerate}
        \item Remain vacant and be filled by election (as per \cref{sec:AGMs}) at the next General Meeting, which must be held within the next 2 weeks.
    \end{enumerate}
    \item No member of Committee may fill two roles simultaneously. Upon being appointed to a second position, they immediately cease to hold the first (and are subject to the rules given by \cref{sec:committee}, \cref{sub:committee_resign}).
\end{enumerate}


\section{General Meetings}
\begin{enumerate}
	\item A General Meeting shall be open to all financial members of the Society.
	\item The quorum of a General Meeting shall consist of twice as many financial members of the Society as there are positions on Committee.
    \item The Committee may, at any time, call a Ordinary General Meeting of the Society.
    \item The Secretary shall call a Special General Meeting upon receiving a written requisition from at least half as many financial members of the Society as are required for quorum.
    \begin{enumerate}
        \item The meeting shall be held no later than 14 days immediately following receipt of such requisition. 
        \begin{enumerate}
            \item If the secretary fails to call the meeting within that time, any of the signatories of the requisition may do so.
        \end{enumerate}
        \item \label{sub:special_meeting_priority} Any business set out in the requisition shall have priority over all other business. 
    \end{enumerate}
    \item The Secretary shall cause written notice of any General Meeting together with that meeting's agenda to be published in a form readily accessible to members at least four days prior to the date appointed for that meeting.
    \begin{enumerate}
        \item This agenda may be changed during the meeting, subject to the restriction in \cref{sub:special_meeting_priority} if appropriate.
    \end{enumerate}
    \item No General Meeting may be held while a Guild General Meeting is in progress, except where the written notice of the meeting was given before the written notice of the Guild General Meeting. Any such meeting being conducted in contravention of this requirement shall disband immediately on the order of a disciplinary officer of the Guild.
    \item All General Meetings of the Society shall be conducted in accordance with the procedures in the Standing Rules and Orders of the Guild Council.
    \item The General Meeting shall, in addition to the powers expressly granted to it by this Constitution, have all powers which are granted to the Committee.
\end{enumerate}


\section{Annual General Meetings of the Society} \label{sec:AGMs}
\begin{enumerate}
    \item The Society shall hold its Annual General Meeting within the first four weeks of each academic year.
    \item The Society may, at the Annual General Meeting, select a patron who, willing to do so, shall hold office until the succeeding Annual General Meeting.
    \item Before the Annual General Meeting, the Secretary shall call for nominations for the offices and Committee of the Society, and shall include the same in the notice of the Annual General Meeting. Nominations shall close at that meeting.
    \item The election of the Committee of the Society shall be conducted by ballot subject to the following conditions:
    \begin{enumerate}
        \item Only financial members of the Society may nominate, vote, or be nominated.
        \item No votes shall be accepted by proxy or in absentia.
        \item All executive office bearers must be full time students at the University and Guild members for the duration of their term.
        \item \label{fresher_rep_requirement} Only Freshers shall be eligible for the position of Fresher Representative.
    \end{enumerate}
\end{enumerate}


\section{Committee Meetings}
\begin{enumerate}
    \item The Committee shall meet as such times and places as the President, in consultation with the other Committee members shall determine.
    \item The quorum of a Committee meeting shall be a simple majority (rounded up) of Committee and of the executive office bearers.
    \item The Committee shall only exercise its powers (as defined in this constitution or in Regulations) at a properly convened meeting of the Committee, except as elsewhere provided in the Constitution.
    \item The Secretary or President shall cause all members of the Committee to receive three days notice of any such meeting including an agenda of the business to be discussed. This agenda may be expanded upon during the meeting.
    \begin{enumerate}
        \item A meeting may be called without this notice if a two-thirds majority (rounded up) of Committee and of the executive office bearers are present.
    \end{enumerate}
    \item The Secretary shall forthwith call a Special Committee Meeting upon receiving a written requisition from at least two Committee members.
    \begin{enumerate}
        \item Any such Special Meeting shall be held not later than seven days immediately following the receipt of such requisition.
        \begin{enumerate}
            \item If the Secretary fails to call the meeting within that time, any one of the members signing the requisition may do so. 
        \end{enumerate}
        \item Any business set out in the requisition shall have priority over all other business.
    \end{enumerate}
    \item All meetings of the Committee shall be conducted in accordance with the procedures prescribed in the Standing Rules and Orders of the Guild Council.
    \item Subject to this Constitution, the Committee shall be responsible for giving effect to the objectives of the Society (see \cref{sec:objectives}) and for carrying on its everyday business.
    \item Towards this end, the Committee shall have the power to:
    \begin{enumerate}
        \item Acquire and dispose of property, dispose of money, open banking accounts, and enter into contracts.
        \begin{enumerate}
            \item The Committee shall not borrow money or incur debts or liabilities on behalf of or in the name of the Society to an amount greater than five dollars per existing financial member of the Society.
        \end{enumerate}
        \item Make Regulations for the orderly and proper management of the affairs of the Society.
        \begin{enumerate}
            \item So long as no Regulation is in conflict with the word or spirit of this Constitution.
        \end{enumerate}
        \item Impose fines for the breach of this Constitution or Regulations.
    \end{enumerate}
    \item These powers are in addition to any other powers given in this Constitution (in particular, see \cref{sec:member_suspension}).
\end{enumerate}


\section{Duties and Powers} \label{sec:duties}
\begin{enumerate}
    \item The President shall have the following duties and powers, in addition to those elsewhere in the Constitution and in any Regulations: \label{sub:pres_duties}
    \begin{enumerate}
        \item To coordinate and supervise the work of the Committee.
        \item To carry out the will of the Society.
        \item To chair Committee and General Meetings of the Society.
        \item When immediate action is required in any matter affecting the interests of the society: \label{sub:exec_power}
        \begin{enumerate}
            \item To take such actions upon seeking the advice and agreement of another member of the Committee (preferably the Vice-President).
            \item Any actions taken as such, shall be subject to review at the next Committee meeting. 
        \end{enumerate}
    \end{enumerate}
    
    \item The Vice-President shall have the following duties and powers, in addition to those elsewhere in the Constitution and in any Regulations:
    \begin{enumerate}
        \item Assisting the President wherever possible. 
        \item Whenever the President is unavailable, to take on the duties and powers of the President as detailed in \cref{sec:duties}, \cref{sub:pres_duties}.
    \end{enumerate}
    
    \item The Treasurer shall have the following duties, in addition to those elsewhere in the Constitution and in any Regulations:
    \begin{enumerate}
        \item To keep proper books of account dealing with the property and finances of the Society and to furnish the Committee with such information upon request.
        \item To arrange and be responsible for the handling of the petty cash.
        \item To prepare a financial statement detailing income and expenses during their term of office, for presentation at the Annual General Meeting.
        \item To produce and deliver all necessary books, vouchers and other documents to the persons appointed by the Guild for the purpose of conducting and audit, insofar as such persons require.
        \item To produce and deliver all necessary books, receipts and other documents to the persons appointed by the Guild for the purpose of obtaining grants, insofar as such persons require.
    \end{enumerate}
    
    \item The Secretary shall have the following duties, in addition to those elsewhere in the constitution and in any Regulations:
    \begin{enumerate}
        \item To record and distribute all proceedings of the Society in all meetings.
        \item To provide the Guild with information about the Society, upon request.
        \item To keep record of all Society members, and their contact information.
        \item To keep record of any members granted special powers, rights, or responsibilities by Committee.
        \item To keep record of any Regulations passed by Committee.
    \end{enumerate}
    
    \item The Fresher Representative shall have the following duties, in addition to those elsewhere in the constitution and in any Regulations:
    \begin{enumerate}
        \item To look out for the needs and rights of the Freshers.
        \item To be aware of, and acquainted with all Freshers of the Society, insofar as is possible.
        \item To be involved, insofar as is possible, in any Fresher targeted activity the Society may run.
    \end{enumerate}
    
    \item Should any of the Committee members be temporarily unable to fulfill their duties, as defined above, another willing member of Committee shall, at the request of Committee take on some or all of there duties. For example: If the Secretary has vanished, the Committee may ask the President to call a Special General Meeting).
\end{enumerate}


\section{Finances} \label{sec:finances}
\begin{enumerate}
	\item All monies due and payable to the Society shall be received by the Treasurer who shall lodge them without undue delay in the Society Banking Account for the credit of the Society.
    \item Any two Committee members shall be empowered to jointly sign or otherwise approve forms of authority for the withdrawal of any money from the the Society's Banking Account.
    \item \label{sub:petty_budget} The Committee may define a weekly budget from which the Treasurer may authorise the purchasing of consumables. These payments are subject to review by Committee.
    \item \label{sub:printing_budget} Any Committee member may make payments for printing on behalf of the Society. These payments are subject to review by Committee.
    \item With exception of the consumable and printing payments (\cref{sec:finances}, \cref{sub:petty_budget,sub:printing_budget}), and the executive power of the President (\cref{sec:duties}, \cref{sub:pres_duties}), no payments shall be made on behalf or in the name of the Society unless it has been authorized by the Committee.
\end{enumerate}

\section{Major Obligations to the Guild} \label{sec:guild_obligations}
\begin{enumerate}
    \item The Society shall comply with the rules of the Guild and the Societies Council of the Guild, and all other provisions enrolled upon the Guild Statutes Book.
    \begin{enumerate}
        \item The committee shall be responsible for such compliance.
    \end{enumerate}
    \item Such rules supersede the Regulations of the Society, and this Constitution, if and where contradiction occurs.
\end{enumerate}

\section{Suspension of Members} \label{sec:member_suspension}
\begin{enumerate}
    \item The Committee has the ability to suspend any member if they believe it in the best interests of the Society. Such suspensions shall be reviewed at the next General Meeting of the Society.
    \item While suspended the member shall be unable to exercise any right as a member. 
    \item The Committee, or General Meeting, may discontinue suspension and restore a member to normal standing, or to impose other sanctions. (Such as expulsion (see \cref{sec:expulsion}) or continued suspension for a fixed amount of time.)
    \item \label{committee_suspended} If for any reason a Committee member is suspended, a General Meeting must be held within two weeks to resolve the situation.
\end{enumerate}


\section{Expulsion of Members\label{sec:expulsion}}
\begin{enumerate}
    \item The General Meeting may, by two-thirds majority vote, expel any member or associate.
    \item While expelled the former member or associate shall be unable to exercise any right as a member. 
    \item Once expelled the former member or associate remains expelled and is barred from membership for all time.
    \item Expulsion can be repealed by a two-thirds majority vote of a General Meeting.
\end{enumerate}


\section{Availability of Constitution}
\begin{enumerate}
	\item This Constitution shall be made available to members on request.
\end{enumerate}


\section{Alteration of Constitution}
\begin{enumerate}
    \item To amend this Constitution, the following steps must be taken:
    \begin{enumerate}
        \item Any two financial members of the Society may not less than four days before the day appointed for the next General Meeting submit to the Secretary a notice of motion by them proposing an alteration to the Constitution.
        \item The motion may then be considered by the Society at it next General Meeting and amendments which are relevant to the subject matter thereof may be moved without notice.
        \item The motion or any amendment thereto shall be deemed adopted if it receives a two-thirds majority of the General Meeting.
        \item The motion as adopted with any amendments shall come into force upon receiving the approval of the Societies Council of the Guild.
    \end{enumerate}
    \item A history of revisions of this Constitution shall be maintained in \cref{app:history}. Where possible the Committee shall maintain details of these revisions and 
\end{enumerate}


\section{Dissolution} \label{sec:dissolution}
\begin{enumerate}
    \item In the event of the Society's disaffiliation to the Societies Council of the Guild \emph{and} cessation of activity, the resources of the Society shall be given into the holding of the University Computer Club.
    \begin{enumerate}
        \item This is given with the understanding that upon the formation of a club of similar spirit and objectives (see \cref{sec:objectives}) to the Society, as judged by the University Computer Club, comes into being, that these resources shall be passed on to them.
    \end{enumerate}
    \item In the event of University Computer Club no longer existing at the time of the Society's dissolution, the resources of the Society shall be given into the holding of the Societies Council of the Guild.
    \begin{enumerate}
        \item This is given with the understanding that upon the formation of a club of similar spirit and objectives (see \cref{sec:objectives}) to the Society, as judged by the Societies Council of the Guild, comes into being, that these resources shall be passed on to them.
    \end{enumerate}
\end{enumerate}

\appendixpage

\appendix \section{History of this Constitution} \label{app:history}

\noindent Prepared by Andrew ``Gozz'' Gozzard, with the assistance of Lyndon ``Frames'' White. Drawing upon the Unigames constitution.

\medskip{}

\begin{itemize}
	\item[] Adopted by General Meeting on 2017-03-21
    \item[] Revisions adopted by General Meeting on 2018-03-??
\end{itemize}

\medskip{}

\noindent As witnessed by:
\begin{description}
\item [{President:}] TBA \hrulefill
\item [{Vice-President:}] TBA \hrulefill
\item [{Treasurer:}] TBA \hrulefill
\item [{Secretary:}] TBA \hrulefill
\end{description}

\end{document}
